### 2021-07-03 docs/manuscript/manuscript.tex
Add number of multi-input topologies

We found the presence of network motifs in the set of GRNs produced by the
genetic algorithm. However, we also found a great diversity of network
topologies that could produce a striped gene expression pattern.\\

>>>>

We found the presence of network motifs in the set of GRNs produced by the
genetic algorithm. However, we also found a great diversity of network
topologies that could produce a striped gene expression pattern, where 615 out of
714 were multi-input topologies, showing that considering multiple
morphogen inputs allows to find different solution for the patterning
problem.\\
